---
title: "mEPSC One-Way ANOVA - Amplitude"
output: html_notebook
---
```{r set-options, echo=FALSE, cache=FALSE}
library(knitr)

```

Author: Haley E. Speed, Ph.D
Date: 07-10-17
Project: example

<hr>
<h2>Group Definitions </h2>
<hr>
<li>Group1 = Oil + Saline vs Oil + IGF-1
<li>Group2 = Oil + Saline vs CPF + Saline
<li>Group3 = Oil + Saline vs CPF + IGF-1
<li>Group4 = Oil + IGF-1 vs CPF + Saline
<li>Group5 = Oil + IGF-1 vs CPF + IGF-1
<li>Group6 = CPF + Saline vs. CPF + IGF-1
<br>


```{r}
#Load in the data from a CSV file
#Each column in the file should contain the average values for each bin

amp <- read.csv("mEPSC_anova.csv")

```
<br>
<hr>
<h2>Descriptive Statistics</h2>
<hr>


```{r}
# Remove "NA" from data

os_amp <- amp$os_amp[!is.na(as.numeric(amp$os_amp))]
oi_amp <- amp$oi_amp[!is.na(as.numeric(amp$oi_amp))]
cs_amp <- amp$cs_amp[!is.na(as.numeric(amp$cs_amp))]
ci_amp <- amp$ci_amp[!is.na(as.numeric(amp$ci_amp))]

# Get sample size
os_n <- length(os_amp)
oi_n <- length(oi_amp)
cs_n <- length(cs_amp)
ci_n <- length(ci_amp)

# Get mean
os_mean <- mean(as.numeric(os_amp))
oi_mean <- mean(as.numeric(oi_amp))
cs_mean <- mean(as.numeric(cs_amp))
ci_mean <- mean(as.numeric(ci_amp))

# Get SD
os_SD <- sd(as.numeric(os_amp)) 
oi_SD <- sd(as.numeric(oi_amp))
cs_SD <- sd(as.numeric(cs_amp))
ci_SD <- sd(as.numeric(ci_amp))

# Get SE
os_SE <- os_SD/sqrt(os_n)
oi_SE <- oi_SD/sqrt(oi_n)
cs_SE <- cs_SD/sqrt(cs_n)
ci_SE <- ci_SD/sqrt(ci_n)

# Assemble easy-to-read table
desc_stats <- matrix(c("Oil + Saline", "Oil + IGF-1", "CPF + Saline", "CPF + IGF-1", os_mean, oi_mean, cs_mean, ci_mean, os_SE, oi_SE, cs_SE, ci_SE, os_n, oi_n, cs_n, ci_n),nrow = 4, ncol = 4)
colnames(desc_stats) <- c("Group", "Mean", "SE", "n")

# Print results table without quotation marks
print (kable(as.data.frame(desc_stats), digits = 2))


```


<br>
<hr>
<h2>One-Way ANOVA on total mEPSC Amplitude for each pair of groups</h2>
<hr>


<b>For Oil+Saline vs Oil+IGF-1:</b>

```{r}

# 1. Fit the model first (One Way ANOVA, Completely Randomized Design)
# 2. diagnostic plots
# 3. If data fit a normal distribution (Q-Q), evaluate the model effects

fit1 <-aov(amp1 ~ groups1, data = amp)  # Analysis of Variance
table1 <-summary(fit1)                  # Gives summary information from fit 3 (df, F, sum, p)
table2 <- drop1(fit1,~.,test="F")       # drops redundant information from fit 3
print(table1)                           # The info we will use for reporting

```


<hr>
<h2>Plots for One-Way ANOVAs</h2>
<hr>

<b>For Oil+Saline vs Oil+IGF-1:</b>
```{r}

plot(fit1) 

```


